\section{Projects}

\resumeSubHeadingListStart
    \resumeSubheading
    {ADNU RACER}{Jun 2024 -- Sep 2024}
    {Backend Developer/Database Designer}{Oracle}
    \resumeItemListStart
        \resumeItem{Contributed to the design of the newly approved system's database schema by developing the conceptual model and wrote the SQL scripts for database creation.}
        \resumeItem{Contributed to creating system privileges and roles to ensure access control and data security to the system.}
    \resumeItemListEnd
    % ------------------------------------------------------------------------------------------ %
    \resumeSubheading
    {STUBU.AI}{Oct 2023 -- Apr 2024}
    {Lead Frontend Web Developer}{React, TailwindCSS, Typescript, NodeJS, MongoDB, ExpressJS}
    \resumeItemListStart
        \resumeItem{Lead front-end developer for STUBU.AI -- an AI-powered Learning Management System that adapts to learners as an all-in-one study buddy turning education into a personalized and interactive experience; reinventing the traditional education system.}
        \resumeItem{Assisted on UI/UX Design and made improvements to user experience (UX).}
        \resumeItem{Lead the project management for the front-end team consisting of four (4) developers and conducted SCRUM meetings for the group.}
        \resumeItem{Utilized version control and project management tools such as ClickUp and Github for efficient collaboration and tracking of project progress.}
        \resumeItem{Conducted code reviews to the team developers and provided technical documentations upon submission for Appcon 2023}
    \resumeItemListEnd
    % ------------------------------------------------------------------------------------------ %
    \resumeSubheading
    {aiProof}{Mar 2024 -- May 2024}
    {Mobile Developer}{Flutter, Dart, Firebase}
    \resumeItemListStart
        \resumeItem{Lead Project Manager of a two-person project.}
        \resumeItem{A convenient mobile application tool for scanning and AI proofing written documents.}
        \resumeItem{Developed core features of the applications e.g., OCR, statistics, and home page.}
        \resumeItem{Configured and setup back-end requirements for the Rapid API Integration for AI proofing.}
        \resumeItem{UI/UX Engineer responsible for developing responsive and custom made design for an overall user experience.}
    \resumeItemListEnd
    % ------------------------------------------------------------------------------------------ %
    \resumeSubheading
    {eBayan}{Sept 2023 -- Dec 2023}
    {Mobile Developer}{Flutter, Dart, Firebase}
    \resumeItemListStart
        \resumeItem{An intuitive barangay-to-community mobile application for announcement creation management system.}
        \resumeItem{Project manager of the entire project of a two-person project.}
        \resumeItem{Developed core features of the application e.g., management system, authentication, and back-end configuration to google services -- firebase, firestore, and firebase authentication.}
        \resumeItem{UI/UX engineer responsible for developing responsive and custom made design for an overall user experience.}
    \resumeItemListEnd
    % ------------------------------------------------------------------------------------------ %
    \resumeSubheading
    {Dadsbol}{Apr 2024 -- May 2024}
    {Lead Game Programmer}{Unity, C\#}
    \resumeItemListStart
        \resumeItem{Lead the development of the game; a physics-based 3D ragdoll power dodgeball game. that allowed the team to stay on track of the short deadline. Developed the game's core mechanics and gameplay; Designed the game's UI/UX.}
        \resumeItem{Developed the game's AI and enforced project architecture through simulation tick-based event system that allowed for clean modularized code.}
        \resumeItem{Utilized version control and project management tools such as Trello and Github for efficient collaboration and tracking of project progress.}
        \resumeItem{Collaborated with cross-functional teams to gather requirements, work on strengths, and ensure smooth integration and development for the game.}
    \resumeItemListEnd
\resumeSubHeadingListEnd